 

### 2021-09-01 vertical-thermal-review_SI.Rmd
reinstate lit review methods appendix
issue #53

#Appendices
appendix_NEON_methods <- "S1"
appendix_tealeaves_methods <- "S2"

appendix_NEON_methods_title<- "Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods for leaf energy balance modeling"

@@

>>>>

# SI
## appendices

appendix_NEON_methods <- "S1"
appendix_tealeaves_methods <- "S2"
appendix_lit_review_methods <- "S3"

appendix_NEON_methods_title<- "Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods for literature review"

@@

\newpage
# `r appendix_lit_review_methods_title`
